MONID

### 2023-09-20 Presentation/presentation.tex
update

    \begin{block}{Note.}    
        The difference between maximal and minimal interpretation becomes important only when we are evaluating the at the boundaries of a trace; $\underline{\text{max}}$ rules evaluates at $\underline{\text{true}}$ at initial and final istants, while $\underline{\text{min}}$ rules evaluates at $\underline{\text{false}}$.
    \end{block}    
    \newpage
    To better understand the mechanism, let us introduce an example.\\ Given the definition 
    \begin{align*}
        & \underline{\text{min}}\ \mathtt{Property}(\underline{\text{Form}}\ F) =F \lor \bigcirc \mathtt{Property}(F)
    \end{align*} 
    and the sequence $\sigma=\alpha_{1},\ldots ,\alpha_{n}$, $\mathtt{Property}$ will evaluate to \textit{true} 
    \begin{align*}
        & evaluate(\ldots evaluate(evaluate(\mathtt{Property},\alpha_1),\alpha_2),\ldots,\alpha_n)=true
    \end{align*}
    if and only if the rule is true at some given event $\alpha_i$. Once the sequence has been completely analyzed, we will obtain the following big disjunction: 
    \begin{align*}
        & F \lor \bigcirc(F \lor \bigcirc(\ldots F \lor \bigcirc \mathbf{Property(F)})) 
    \end{align*}
    $\mathbf{Property(F)}$ will be evaluated as false since it is the last of a big disjunction and we want to close it.

@@

    \includegraphics[scale=0.22]{images/semantics.png}
\end{frame}

@@

\begin{frame}
    \frametitle{Smurf Attacks}
    A \textit{smurf attack} is a DDoS attack targeting computer networks by sending large volumes of ICMP echo request packets to a broadcast address. The attacker spoofs the source IP address to make it appear as originating from the victim's IP address, causing all devices to respond with ICMP echo replies.\\
    \vspace{2.5mm}
    In this example we will use \textit{tcpdump} to obtain the logs from the network interface; the formula that describes the absence of the attack is the following:
    \begin{align*}
        & \underline{\text{max}}\ \mathtt{SmurfAttack()} = (type = \text{"ICMP"})\land isBroadcast(ip) \\
        & \underline{\text{mon}}\ \mathtt{SmurfSafety} =\ \mathtt{Always}(\neg\ \mathtt{SmurfAttack()}) 
    \end{align*}
    where \textit{isBroadcast}() checks whether the source’s IP address is a broadcast ip, i.e. all the host bits are set to 1.
\end{frame}

>>>>

    \begin{block}{Note.}    
        The difference between maximal and minimal interpretation becomes important only when we are evaluating the at the boundaries of a trace: $\underline{\text{max}}$ rules evaluates at $\underline{\text{true}}$ at initial and final istants, while $\underline{\text{min}}$ rules evaluates at $\underline{\text{false}}$.
    \end{block}    
    \newpage
    To better understand the mechanism, let us introduce an example.\\ Given the definition 
    \begin{align*}
        & \underline{\text{min}}\ \mathtt{Property}(\underline{\text{Form}}\ F) =F \lor \bigcirc \mathtt{Property}(F)
    \end{align*} 
    and the sequence $\sigma=\alpha_{1},\ldots ,\alpha_{n}$, $\mathtt{Property}$ will evaluate to \textit{true} 
    \begin{align*}
        & evaluate(\ldots evaluate(evaluate(\mathtt{Property},\alpha_1),\alpha_2),\ldots,\alpha_n)=true
    \end{align*}
    if and only if the rule is true at some given event $\alpha_i$. Once the sequence has been completely analyzed, we will obtain the following big disjunction: 
    \begin{align*}
        & F \lor \bigcirc(F \lor \bigcirc(\ldots F \lor \bigcirc \mathbf{Property(F)})) 
    \end{align*}
    $\mathbf{Property(F)}$ will be evaluated as false since it is the last of a big disjunction and we want to close it.

@@

    \includegraphics[scale=0.27]{images/semantics.png}
\end{frame}

@@

\begin{frame}
    \frametitle{Smurf Attacks}
    A \textit{smurf attack} is a DDoS attack targeting computer networks by sending large volumes of ICMP echo request packets to a broadcast address. The attacker spoofs the source IP address to make it appear as originating from the victim's IP address, causing all devices to respond with ICMP echo replies.\\
    \vspace{2.5mm}
    In this example we will use \textit{tcpdump} to obtain the logs from the network interface; the formula that describes the absence of the attack is the following:
    \begin{align*}
        & \underline{\text{max}}\ \mathtt{SmurfAttack()} = (type = \text{"ICMP"})\land isBroadcast(ip) \\
        & \underline{\text{mon}}\ \mathtt{SmurfSafety} =\ \mathtt{Always}(\neg\ \mathtt{SmurfAttack()}) 
    \end{align*}
    where \textit{isBroadcast}() checks whether the destination’s IP address is a broadcast ip, i.e. all the host bits are set to 1.
\end{frame}
